---
title: "Casa0023 week 2"
subtitle: "<br/>Overview of Landsat-8"
author: "Atsumi Hirose"
institute: "University College London CASA"
date: "2023/01/17 (updated: `r Sys.Date()`)"
output:
  xaringan::moon_reader:
    lib_dir: libs
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
---

```{r echo=FALSE}
library(RefManageR)
BibOptions(check.entries = FALSE,
           bib.style = "authoryear",
           cite.style = "authoryear",
           style = "markdown",
           hyperlink = TRUE,
           dashed = FALSE,
           no.print.fields=c("doi", "url", "urldate", "issn"))
myBib <- ReadBib("./references.bib", check = FALSE)
```

---

# Summary

## Overview of Landsat 8

-   Launched on 11th February 2013

-   Collect an archive of medium resolution multispectral image data

-   Initially planned for not less than 5 years

-   Aims \> Data consistent with data from the earlier Landsat missions and \> Distribution of Landsat data products to the public

---

# Major technological feature of Landsat-8

## Pushbroom technology

-   being able to dwell longer on a particular part of the terrain

-   no moving mirror

-   Thus more accurate measurement

---
# Two Sensors of Landsat-8 (1)
## Operational Land Imager (OLI)
- Multispectral sensor including:
> visible
> near infrared and 
> shortwave infrared portions (band 1 through 9)

- The additional bands for water and clouds detection

- Collection of land-surface data 

- Spatial resolution 
> 15m x 15 m (panchromatic) and 
> 30m x 30 m (multispectral), 
> consistent with previous missions (Landsat TM of Landsat 4 and Landsat 5 and ETM+ of Landsat 7) 

---

# Two Sensors of Landsat-8 (2)

## Thermal infrared sensor (TIRS)

-   Two long wavelength bands (band 10 and band 11)

-   Collection of land surface temperature

-   Spatial resolution at Nadir of 100 m x 100 m

---

# Application (1)

## Automatically map land cover features

-   Urban built-up areas are mapped:
-   Methods include:

1.  Using the normalised difference built-up index (NDBI), or

2.  Modifications of the NDBI (eg. `r Citet(myBib,"bhatti2014built")` or `r Citet(myBib,"bouhennache2019new")`)

---

# Application (2)

## Landsat-8 TIRS to retrieve Land Surface Temperature (LST).

-   `r Citet(myBib,"jimenez2014land")` take advantage of the thermal infrared sensors on board Landsat-8

-   'Split-window' algorithm to retrieve LST

---

# Reflection

-   Lots of modelling/transformation needed to derive the information required for various purposes \> eg earth surface temperature or urban built-up areas

-   I have seen 'built-up' grid used in global health research to understand the effect of urbanisation on health (or the association between urbanisation and health outcomes).

-   Those studies are actually looking at the association between the Normalised Difference Built-up Index and health outcomes as a proxyn for 'urbanisation'.

---

## References

```{r refs, echo=FALSE, results="asis"}
PrintBibliography(myBib)
```
